Trauma treatment delay

### 2023-12-15 manuscriptlongversion.Rmd
text

When looking at the patient demographics, it is clear that the majority
admitted to trauma care are men, with it being slightly higher in the
delay to treatment group. However, not high enough to be statistically
significant. The fact that gender did not show an increased odds ratio
should be seen as a positive sign. It suggests that among trauma
patients, there is no systematic delay based on this patient level
factor.

@@

Further analysing the results and it's clinical applications, the
results can be interpreted as that it is mostly injured and less awake
patients that receive delayed. The clinical applications for this are
not clear, but caregivers should already be aware that the more injuries
a patients has, the more room for error exists. It is good though to
receive a reminder that it's important to always work towards minimizing
the delay for these injured patients.

Further analysing the results and it's clinical applications, the
results can be interpreted as that it is mostly injured patients with
affected consciousness that receive delayed treatment.

>>>>

@@

Further analysing the results and it's clinical applications, the
results can be interpreted as that it is mostly injured patients with
affected consciousness that receive delayed treatment. The clinical
applications of this can be seen as we need to do more to avoid this
delay for this patient group. If clinicians are aware of that these
patients receive delayed treatment more frequently, active steps can be
taken towards reducing this risk and bettering the trauma care.

Regarding health equity when looking at the patient demographics, it is
clear that the majority admitted to trauma care are men, with it being
slightly higher in the delay to treatment group. However, not high
enough to be statistically significant. The fact that gender did not
show an increased odds ratio should be seen as a positive sign. It
suggests that among trauma patients, there is no systematic delay based
on this patient level factor.
